The Babyname In USA
========================================================

On my 25th birthday,I strolled in the gitHub.I find a research about the babynames from the 1880 to 2008,the author list a list about a thousand babynames which are used most.He wants to see the  1000 names include the percent the whole the country babynames.
It is interesting to find the 1000 boynames decreasing slower than the girls'.To the 2008,the 1000 boynames still include at least 80% the whole boynames in the state.But the girls' has decreased to about 68%.
I want to find the most used babynames in the 2008.
```{r}
babyname=read.csv("F:/苏建冲出品/数据集/babynames/baby-names.csv",header=T)
head(babyname)
baby2008=babyname[babyname[,1]=="2008",]
boy2008=baby2008[baby2008$sex=="boy",]
girl2008=baby2008[baby2008$sex=="girl",]
btop2008=boy2008[order(boy2008$percent,decreasing=T),]
head(btop2008,10)

```
So,Jacob is the champion.There is a boy named Jacob in one hundred boys.The other most used boynames in 2008 are Michael,Ethan,Joshua,Daniel and Alexander.
It is quite funny in the hot US TV series _LOST_,Jacob ,Michael,Ethan and Daniel all there.
Maybe when make the TV series story,the maker has pay the attention the research.
Maybe the most babynames research is quite useful for our life!
How sex the finding!
Next to the girls
```{r}
gtop2008=girl2008[order(girl2008$percent,decreasing=T),]
head(gtop2008,10)
```
The most used girlnames are Emma,Isabella,Emily,Madison and Ava.

Haha,i thought the "Jack" and "Rose" will win the games.
Now i will find the order the "Jack"and"Rose".

```{r}
which(btop2008$name=="Jack")
btop2008[which(btop2008$name=="Jack"),]
which(gtop2008$name=="Rose")
btop2008[which(gtop2008$name=="Rose"),]
```
Wooe."Jack" ranks the 39,"Rose" is far away from the "Jack",she ranks the 334.

Ok,let us do it again in the 1880.

```{r}
baby1880=babyname[babyname[,1]=="1880",]
boy1880=baby1880[baby1880$sex=="boy",]
girl1880=baby1880[baby1880$sex=="girl",]
btop1880=boy1880[order(boy1880$percent,decreasing=T),]
head(btop1880,10)
gtop1880=girl1880[order(girl2008$percent,decreasing=T),]
head(gtop1880,10)
```
John,James,Charles are still in the _LOST_.
Where are the "Jack" and "Rose"?
```{r}
which(btop1880$name=="Jack")
btop2008[which(btop1880$name=="Jack"),]
which(gtop1880$name=="Rose")
btop2008[which(gtop1880$name=="Rose"),]

```
####Jack is 77,and Rose is 30.Compare to 2008,Jack is 39,Rose is 334.
"Rose" had made a huge change in the history of girlnames.She also made the farther distance to Jack.What a pity about _Titanic_!




